---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  fig.path = "man/figures/README-",
  fig.align = "center",
  out.width = "100%",
  collapse = TRUE,
  comment = "#>"
)
```

# kerasgenerator <img src="man/figures/logo.svg" align="right" height=140/>

`kerasgenerator` package is shipped with some data generator functions, which are designed to make the data generation process for [`keras`](https://keras.rstudio.com) models easier.

# Getting Started

## Installation

The package is in early development stage and currently only available via GitHub. You can install the development version using [`install_github()`](http://devtools.r-lib.org/reference/install_github):

```{r, eval=FALSE}
# install devtools first if you haven't
if (!require(devtools)) install.packages("devtools")

# install the development version from GitHub
devtools::install_github("bagasbgy/kerasgenerator")
```

## Compatibility

Most of `kerasgenerator` functionalities are using `dplyr` and `recipes` interface to make data preparation process easier. Note that you must import `kerasgenerator` after `keras` library imported to make the package works properly:

```{r}
# import libs
library(dplyr)
library(keras)
library(kerasgenerator)
library(recipes)
```

## Designing a generator

Let's make a quick example using `iris` dataset. For a simple model that use cross-sectional data, you can start by using `data_generator()` to convert the data into pre-compiled generator:

```{r}
# initiate a generator
gen <- set_generator(
  data = iris,
  batch_size = 32,
  shuffle = TRUE
)

gen
```

The pre-compiled generator is partially-compatible with `dplyr` and `recipes` API. For example, you can create the dummy variables and do some preprocessing using `recipes`, and add some feature engineering using `mutate`:

```{r}
# create a recipes
rec <- recipe(Species ~ . - Species, iris) %>%
  step_mutate(
    Petal.Ratio = Petal.Length / Petal.Width,
    Sepal.Ratio = Sepal.Length / Sepal.Width
  ) %>%
  step_sqrt(all_numeric()) %>%
  step_center(all_numeric()) %>%
  step_scale(all_numeric()) %>%
  step_dummy(all_nominal(), one_hot = TRUE) %>%
  prep()

# store the recipes to generator
gen %>%
  inject_recipe(rec = rec)
```

If you already done with data preprocessing parts, you can declare which variables you want to use as `x` and `y` using `select_x` and `select_y`:

```{r}
gen %<>%
  inject_recipe(rec = rec) %>%
  select_x(-starts_with("Species")) %>%
  select_y(starts_with("Species"))
```

**Note** that I used `%<>%` (assign pipe) from `magrittr` just for efficiency.

Saving the generator after selecting the variables is very recommended, since it makes the following sample splitting process become easier:

```{r}
# sample index
set.seed(1)
intrain <- sample(nrow(iris), nrow(iris) * 0.7)

# split sample using dplyr's slice
train_gen <- gen %>%
  slice(intrain) %>%
  build_generator()

val_gen <- gen %>%
  slice(-intrain) %>%
  build_generator()
```

And now we are ready to test some functionalities in the model fitting process.

## Model fitting using generator

In building Keras model, `kerasgenerator` provided some helpers function for defining some parameters related to the data. This is can be done from `get_meta()` function. For example, you can use `get_meta()` for getting the `input_shape` and `output_shape`:

```{r}
model <- keras_model_sequential() %>%

  layer_dense(
    name = "dense1",
    units = 16,
    input_shape = get_meta(train_gen, "input_shape")
  ) %>%
  
  layer_dense(
    name = "dense2",
    units = 8
  ) %>%
  
  layer_dense(
    name = "dense_output",
    units = get_meta(train_gen, "output_shape"),
    activation = "softmax"
  )

model %>% compile(
  optimizer = "adam",
  metrics = "accuracy",
  loss = "categorical_crossentropy"
)
```

In addition, `kerasgenerator` also masking the `*_generator()` function from `keras` in order to make those functions know the generator characteristic, like the number of `steps_per_epoch`/`steps`, and by default the `*_generator()` will use it as default parameters unless you want to override it manually.

For example, when fitting using `kerasgenerator`, you just need to pass the generator(s) and it will automatically recognize the generator(s):

```{r}
history <- model %>% fit_generator(
  generator = train_gen,
  validation_data = val_gen,
  epochs = 30
)

plot(history)
```

Note that `predict_generator` also provided `label` option to specify whether the prediction output should be tidied. The default value for this option is set to `TRUE`:

```{r}
model %>% evaluate_generator(val_gen)

model %>% predict_generator(val_gen)
```

## Further Development

* Support for generating data from **file(s) in specified path**
* Data generator for **k-shot learning** model fitting
