---
output: github_document
---

```{r setup, include = FALSE}

knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  fig.path = "man/figures/README-",
  fig.align = "center",
  out.width = "100%"
)

```

# kerasgenerator <img src="man/figures/logo.svg" align="right" height=140/>

`kerasgenerator` package is shipped with some data generator functions, which are designed to make the data generation process for [`keras`](https://keras.rstudio.com) models easier.

# Getting Started

## Installation

The package is in early development stage and currently only available via GitHub. You can install the development version using [`install_github()`](http://devtools.r-lib.org/reference/install_github):

```{r, eval=FALSE}

# install devtools first if you haven't
if (!require(devtools)) install.packages("devtools")

# install the development version from GitHub
devtools::install_github("bagasbgy/kerasgenerator")

```

## Compatibility

Most of `kerasgenerator` functionalities are using `dplyr` and `recipes` interface to make data preparation process easier. Note that you must import `kerasgenerator` after `keras` library imported to make the package works properly:

```{r}

# import libs
library(dplyr)
library(keras)
library(kerasgenerator)
library(recipes)

```

## Usage

Let's make a quick example using `iris` dataset. For a simple model that use cross-sectional data, you can start by using `data_generator()` to convert the data into pre-compiled generator:

```{r}

gen <- data_generator(iris, batch_size = 32, shuffle = TRUE)

gen

```



## Further Development

* Support for generating data from **file(s) in specified path**
* Data generator for **k-shot learning** model fitting
